Creating frames of reference for chert exploitation during the Late Pleistocene in Southwesternmost Iberia.

### 2022-10-24 analysis/paper/paper.Rmd
- Corrected draft - Added photos used for plates

library(ggplot2)
theme_set(theme_bw())
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(readr)
library(ggspatial)
library(ggrepel)
library(dplyr)
library(kableExtra)
library(flextable)
library(data.table)
library(tidyr)

@@

@@

ggplot(data = europe_cropped) +
  geom_sf() +
  geom_point(data = chertfield, aes(x = long, y = lat, shape = State, color = State), size = 4) +
  #geom_label_repel(data = chertsamples, aes(long, lat, label=NewCode), box.padding = 0.5, max.overlaps = 30) +
  annotation_scale(location = "br", width_hint = 0.5) +
  annotation_north_arrow(location = "br", which_north = "true", 
        pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_fancy_orienteering)
  #coord_sf(xlim = c(long_min, long_max), ylim = c(lat_min,lat_max), expand = FALSE)

>>>>

library(ggplot2)
theme_set(theme_bw())
library(sf)
library(raster)
library(spData)
library(rnaturalearth)
library(rnaturalearthdata)
library(readr)
library(ggspatial)
library(ggrepel)
library(dplyr)
library(kableExtra)
library(flextable)
library(data.table)
library(tidyr)
library(tmap)

install.packages("tmap")

@@

```{r map, echo=FALSE}

@@

ggplot(data = europe_cropped) +
  geom_sf() +
  geom_point(data = chertfield, aes(x = long, y = lat, shape = State, color = Age), size = 4) +
  #geom_label_repel(data = chertsamples, aes(long, lat, label=NewCode), box.padding = 0.5, max.overlaps = 30) +
  annotation_scale(location = "br", width_hint = 0.5) +
  annotation_north_arrow(location = "br", which_north = "true", 
        pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_fancy_orienteering)
  #coord_sf(xlim = c(long_min, long_max), ylim = c(lat_min,lat_max), expand = FALSE)
